Exploratory Plots

### 2020-11-08 exploratory/2020-10/sub2_fit_dbs.Rmd
Reorganize notebooks

### Performance as measured by MCC
```{r fit_db_sensspec}
sensspec_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) 
sensspec_clust <- read_tsv(here('subworkflows/1_prep_samples/results/sensspec.tsv')) %>% 
  select(-ref) %>% 
  group_by(dataset) %>% 
  summarize(mean_mcc = mean(mcc))
#sensspec <- bind_rows(sensspec_fit, sensspec_clust)
sensspec_fit %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = mcc, color = dataset)) +
  geom_hline(aes(yintercept = mean_mcc), sensspec_clust) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(dataset ~ ref) +
  labs(caption = "The black line represents the *de novo* clustering mcc score.") +
  theme(legend.position = "None",
        axis.title.x = element_blank(),
        plot.caption = element_markdown())
```

@@

### Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```

>>>>

### Performance as measured by MCC
```{r fit_db_sensspec}
sensspec_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) 
sensspec_clust <- read_tsv(here('subworkflows/1_prep_samples/results/sensspec.tsv')) %>% 
  select(-ref) %>% 
  group_by(dataset) %>% 
  summarize(mean_mcc = mean(mcc))
#sensspec <- bind_rows(sensspec_fit, sensspec_clust)
sensspec_fit %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = mcc, color = ref)) +
  geom_hline(aes(yintercept = mean_mcc), sensspec_clust) +
  geom_boxplot(alpha = 0.5) +
  scale_color_brewer(palette = 'Dark2') +
  #ylim(0.5, 1) +
  facet_wrap('dataset', scales = 'free') +
  labs(caption = "The black line represents the *de novo* clustering mcc score.") +
  theme(#legend.position = "None",
        axis.title.x = element_blank(),
        plot.caption = element_markdown())
```

@@

### Fraction of sequences that map to the reference
```{r fraction_reads_mapped_dbs}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=ref)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_brewer(palette = 'Dark2') +
  facet_wrap("dataset", scales = 'free') +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```
